Community Embeddings with Bayesian Gaussian Mixture Model and Variational Inference\\ \thanks{The reported study was partially supported by RFBR grant \textnumero 20-07-00958. The paper was prepared within the framework of the HSE University Project Group Competition 2020-2022.}

### 2022-05-19 paper-ComE-BGMM-VI.tex
move visual comparison K=15 to first page
sort some figures
👨‍💻 add todos

@@

\begin{table}[htbp]
    \centering
    \caption{Hyperparameters used by \citeauthor{ComE_GH}'s implementation of ComE \cite{ComE_GH}.}
    \label{table:params_ComE}
    \begin{tabularx}{\linewidth}{ l | c | X }
        parameter            & notation & description                                                                     \\
        \hline
        \hline
        number\_walks        & $\gamma$ & number of random walks for each node                                            \\
        \hline
        walk\_length         & $\ell$   & length of each walk                                                             \\
        \hline
        representation\_size & $D$      & dimensionality of the embedding                                                 \\
        \hline
        num\_workers         & \empty   & number of threads                                                               \\
        \hline
        num\_iter            & \empty   & number of overall iterations                                                    \\
        \hline
        com\_n\_init         & \empty   & number of initializations to run on the communtiy embedding model (GMM or BGMM) \\
        \hline
        reg\_covar           & \empty   & regularization coefficient for ensuring positive covariance                     \\
        \hline
        batch\_size          & \empty   & size of the batch                                                               \\
        \hline
        window\_size         & $\zeta$  & windows size used to compute the context embedding                              \\
        \hline
        negative             & $m$      & number of negative samples                                                      \\
        \hline
        lr                   & \empty   & learning rate                                                                   \\
        \hline
        alpha                & $\alpha$ & Trade-off parameter for context embedding                                       \\
        \hline
        beta                 & $\beta$  & Trade-off parameter for community embedding                                     \\
        \hline
        down\_sampling       & \empty   & perform down sampling of common nodes                                           \\
        \hline
        communities          & $K$      & number of communities                                                           \\
    \end{tabularx}
\end{table}

@@

\begin{figure}[htbp]
    \centering
    \begin{subfigure}[b]{.4\linewidth}
        \centering
        \includegraphics[width=1\linewidth]{images/ComE/GMM.png}
        \caption{Non-Bayesian}
    \end{subfigure}%
    \begin{subfigure}[b]{.5\linewidth}
        \centering
        \includegraphics[width=1\linewidth]{images/ComE/BGMM.png}
        \caption{Bayesian}
    \end{subfigure}%
    \caption{Gaussian mixture models in plate notation\protect\footnotemark.}
    \label{fig:GMM_vs_BGMM_plates}
\end{figure}
\footnotetext{By Benwing - Created using LaTeX, TikZ, CC BY 3.0, \url{https://commons.wikimedia.org/w/index.php?curid=18934624}}

@@

\begin{table}[htbp]
    \centering
    \caption{Hyperparameter added to ComE for supporting a BGMM for community embedding \cite{ComE_BGMM_GH}.}
    \label{table:params_ComE_BGMM}
    \begin{tabularx}{\linewidth}{ l | c | X }
        parameter                    & notation & description                               \\
        \hline
        \hline
        weight\_concentration\_prior & $\Gamma$ & Bayesian GMM's weight concentration prior \\
    \end{tabularx}
\end{table}

@@

>>>>

\section{Work Proceeding}

TODO programming language, frameworks, and graphing libraries
It is also worth pointing out the libraries of the data processing language with which calculations were made and graphs were built.
Programming/application software development (libraries for graphs).

@@

\begin{table}[H]
    \centering
    \caption{Hyperparameters used by \citeauthor{ComE_GH}'s implementation of ComE \cite{ComE_GH}.}
    \label{table:params_ComE}
    \begin{tabularx}{\linewidth}{ l | c | X }
        parameter            & notation & description                                                                     \\
        \hline
        \hline
        number\_walks        & $\gamma$ & number of random walks for each node                                            \\
        \hline
        walk\_length         & $\ell$   & length of each walk                                                             \\
        \hline
        representation\_size & $D$      & dimensionality of the embedding                                                 \\
        \hline
        num\_workers         & \empty   & number of threads                                                               \\
        \hline
        num\_iter            & \empty   & number of overall iterations                                                    \\
        \hline
        com\_n\_init         & \empty   & number of initializations to run on the communtiy embedding model (GMM or BGMM) \\
        \hline
        reg\_covar           & \empty   & regularization coefficient for ensuring positive covariance                     \\
        \hline
        batch\_size          & \empty   & size of the batch                                                               \\
        \hline
        window\_size         & $\zeta$  & windows size used to compute the context embedding                              \\
        \hline
        negative             & $m$      & number of negative samples                                                      \\
        \hline
        lr                   & \empty   & learning rate                                                                   \\
        \hline
        alpha                & $\alpha$ & Trade-off parameter for context embedding                                       \\
        \hline
        beta                 & $\beta$  & Trade-off parameter for community embedding                                     \\
        \hline
        down\_sampling       & \empty   & perform down sampling of common nodes                                           \\
        \hline
        communities          & $K$      & number of communities                                                           \\
    \end{tabularx}
\end{table}

TODO hyperparameters GMM
In the article, it is desirable to state in more detail the essence of the work of algorithms, to describe hyperparameters in more detail (where do they come from?)
Where are the hyper parameters from? Node2Vec, EM, VI, ...

@@

\begin{figure}[H]
    \centering
    \begin{subfigure}[b]{.4\linewidth}
        \centering
        \includegraphics[width=1\linewidth]{images/ComE/GMM.png}
        \caption{Non-Bayesian}
    \end{subfigure}%
    \begin{subfigure}[b]{.5\linewidth}
        \centering
        \includegraphics[width=1\linewidth]{images/ComE/BGMM.png}
        \caption{Bayesian}
    \end{subfigure}%
    \caption{Gaussian mixture models in plate notation\protect\footnotemark.}
    \label{fig:GMM_vs_BGMM_plates}
\end{figure}
\footnotetext{By Benwing - Created using LaTeX, TikZ, CC BY 3.0, \url{https://commons.wikimedia.org/w/index.php?curid=18934624}}

@@

\begin{table}[H]
    \centering
    \caption{Hyperparameter added to ComE for supporting a BGMM for community embedding \cite{ComE_BGMM_GH}.}
    \label{table:params_ComE_BGMM}
    \begin{tabularx}{\linewidth}{ l | c | X }
        parameter                    & notation & description                               \\
        \hline
        \hline
        weight\_concentration\_prior & $\Gamma$ & Bayesian GMM's weight concentration prior \\
    \end{tabularx}
\end{table}

TODO hyperparameters BGMM
In the article, it is desirable to state in more detail the essence of the work of algorithms, to describe hyperparameters in more detail (where do they come from?)
Where are the hyper parameters from? Node2Vec, EM, VI, ...

@@

%\visresults{GMM}{15}
%\visresults{BGMM}{15}
